Application

### 2021-10-28 main.Rmd
rewrite application

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=hour_day, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_grid(wknd_wday~group, 
             scales = "free_y", 
             labeller = "label_both") + 
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
wkndwday_group
```

>>>>

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=hour_day, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_grid(group~wknd_wday, 
             scales = "free_y", 
             labeller = "label_both") + 
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
  wkndwday_group
```

### 2021-10-28 main_application.Rmd
rewrite application

@@

hod_group <- data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 5) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
   scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  scale_fill_manual(legend_title, values = c("#E69F00",
  "#009E73","#0072B2", "#D55E00", "grey")) + 
  theme(legend.position = "bottom")

@@

moy_group <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 5) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
   scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) + 
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

```{r combined-groups-js, fig.cap = "The distribution of electricity demand for the clusters across hour-of-day, month-of-year and wknd-wday. The median is represented by a line and the shaded region represents the area between $25^{th}$ and $75^{th}$ percentile. Group 2 and 5 have a stronger hour-of-day pattern, while group 1, 3, 5 have a month-of-year pattern. For wknd-wday differences across different groups are not distinct suggesting that it might not be that important a variable to distinguish different clusters."}
hod_group + moy_group
```

@@

- Discussion

As with any clustering method, things become much more complicated when we consider a larger data set with more uncertainty. The methodology run on several customers together might not be useful to given distinct shapes across granularities. Moreover, the groupings from two different appraoches lead to different results, both of which are useful but needs careful considering the context before choosing one over another. Also, note that the customers chosen here do not have a weekend-weekday effect, which might not be true for all customers in the data set. Ideally there are other groups of customers in the entire dataset which can act as prototypes in our problem. Ideally, if these prototypes are not outliers, we can use them for a classification problem for external validation of the clustering problem.

>>>>

Cluster characterization is a crucial aspect of cluster analysis. Figure ref\{fig:combined-groups-js} depicts the summarized distributions across groups and assists us in characterizing each cluster. All of these may be validated only with further information about the customer. Figure \ref{fig: Groups 2 and 5 show a stronger hour-of-day pattern, whereas groups 1, 3, and 5 show a month-of-year pattern. Differences in wknd-wday between groups are not discernible, implying that it may not be a relevant variable in distinguishing various clusters.

@@

hod_group <- data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 5) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_bw()  +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +
  theme(legend.position = "bottom")

@@

moy_group <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 5) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() + theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +
  theme(legend.position = "bottom") 
```

```{r}
wkndwday_data <- data_group %>% create_gran("wknd_wday") %>% 
  create_gran("hour_day")

ylim1 = boxplot.stats(wkndwday_data$general_supply_kwh)$stats[c(1, 5)]

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=hour_day, y = general_supply_kwh)) +
  #lvplot::geom_lv(aes(fill = as.factor(group)), k=5) +
  geom_boxplot(aes(fill = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.size = 1) + 
  coord_cartesian(ylim = ylim1*1.05)+
  #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
#geom_boxplot(aes(fill = as.factor(group))) +
  #scale_fill_lv() +
 xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
   facet_grid(group~wknd_wday, 
             scales = "free_y", 
             labeller = "label_both") + 
  theme_bw() + theme_application() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00","#CC79A7"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "#CC79A7")) +
  theme(legend.position = "bottom") 
```

```{r combined-groups-js, fig.cap = "The distribution of electricity demand for the clusters across hour-of-day, month-of-year and wknd-wday. Group 2 and 5 have a stronger hour-of-day pattern, while group 1, 3, 5 have a month-of-year pattern. For wknd-wday differences across different groups are not distinct suggesting that it might not be that important a variable to distinguish different clusters."}
(hod_group + moy_group + wkndwday_group) +  plot_layout(guides = "collect")
```

Things become far more complicated when we consider a larger data set with more uncertainty, as they do with any clustering problem. Summarizing distributions across clusters with varied or outlying customers can result in a shape that does not represent the group. Furthermore, combining hetergeneous customers may result in similar-looking final clusters that are not effective for visually differentiating them. It is also worth noting that the wknd-wday behavior in the given case does not characterize any cluster. This, however, will not be true for all of the customers in the data set. If more extensive prototype selection is used, resulting in more comprehensive prototypes in the data set, this method might be used to classify the entire data set into these prototype behaviors. However, the goal of this section was to have a few customers that have significant patterns over one or more cyclic granularities, apply our clustering methodology to cluster them, and demonstrate that the method produces useful clusters.

@@
